---
title: "Info"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

# Theoretical background

We propose a simulation model to roughly estimate plausible values of some directly unobservable characteristics of the spread of the infection of the COVID-19 epidemic in Slovakia.At the moment of this writing we can only use the data series of the numbers of all tests and all confirmed cases, without a single death, and very few confirmed recovered individuals.

This manuscript reflects the current state of a work in progress. The main purpose of
this work is to support some modelling decisions of the governmental Institute of Health Policies of the Slovak Republic and other teams, for instance with respect to the calibration of more complex SIR-type models.

An important requirement of this model is that it is easy to implement and understand
such that it can undergo scrutiny from a broader community of professionals and produce useful results at the early stages of the epidemic.

[__Full text__](http://www.iam.fmph.uniba.sk/ospm/Harman/COR01.pdf)

***

# Technical background

App is powered by engine which code you can see below or [__As.txt__](http://www.iam.fmph.uniba.sk/ospm/Harman/programs/corona_sim.txt) and app lives in [__GitHub__](https://github.com/SamuelHudec/COVID).

```{r script, echo=FALSE, comment="", tidy=TRUE}
read_lines('model2.R')
```

